%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[misc]{ifsym}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Pushpankar Kumar} % Your name
\address{\faEnvelope\hspace{.25em} \href{mailto:pushpankark@gmail.com}{ pushpankark@gmail.com} \faPhone \hspace{.25em} +91-9572222953 \hspace{.5em}\href{https://www.linkedin.com/in/pushpankar}{\faLinkedin}\hspace{.5em} \href{https://github.com/pushpankar}{ \faGithub}} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{(+1)~7hh~9~8486 \\ x@ii.yzac.in} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l @{\hspace{6ex}} l }
Expert &  Natural Language Processing & Pytorch, Python, Linux  \\
Proficient & Computer Vision, Algorithms \& Data structures & Tensorflow, C/C++, Java \\
Beginner & Android development, Web development & JavaScript, SQL, Elixir \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{EdgeNetworks}{May 2018 - Present}{Data Scientist}{}
\item Developed a information retrieval system to rank resumes for a JD and achieved 82.51\% NDCG@20
\item Built a knowledge graph incorporating 30000+ titles, 70000+ skills and 100+ industries.
\item Did knowledge base completion using ComplEx tensor factorization, SVD, and other techniques.
\end{rSubsection}


\begin{rSubsection}{ParallelDots}{July 2017 - May 2018}{Data Scientist}{}
\item Developed a multi-task learning algorithm with self-attention mechanism to classify emotion, intent, and sentiment. Achieved 80\% accuracy for ternary sentiment classification.
\item Implemented a aspect based sentiment classifier and achieved state-of-the-art level accuracy.
\item Improved accuracy of sentiment, emotion, and intent classification by upto 8\% using transfer learning.
\item Develop unsupervised model in Tensorflow to find topics in a document and similar document using LDA2vec.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Paper}
\begin{rSubsection}{\href{https://arxiv.org/abs/1712.05972}{\textbf{Train Once, Test Anywhere: Zero-Shot Learning for Text Classification}  }}{}{}{}
\item Developed a new technique for classifying text by just having the definition of classes.
\item Achieved results comparable to supervised ML techniques and showcased the potential of vast amount of noisy data.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Projects}
\begin{rSubsection}{}{}{}{}
\item Developed group study platform as a part of YCombinator's Startup School program.
\item Developed social media platform for sharing election news and memes using techonologies like Elixir, GraphQL, and ReactJS.
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
% \begin{rSection}{Relevant Courses}
% \itab{\textbf{Core Courses}} \tab{}  \tab{\textbf{Other Courses}}
% \\ \itab{Fluid Mechanics \& its applications } \tab{}  \tab{Computational Methods in Engineering}
% \\ \itab{Thermodynamics} \tab{}  \tab{Fundamental of Computing} 
% \\ \itab{Heat Transfer \& its applications} \tab{}  \tab{Probability and Statistics} 
% \\ \itab{Mass Transfer \& its applications} \tab{} \tab{Calculus \& Linear Algebra}
% \\ \itab{Transport Phenomena (ongoing)} \tab{} \tab{Introduction to Mechanics}
% % \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}
% \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Institute of Technology Srinagar} \hfill {\em August 2013 - July 2017} \\
Metallurgical and Material Engineering  \\
% \\ B.Tech, 7.2 CGPA \\
\\
{\bf Udacity } \hfill {\em Dec 2016 - Feb 2017}\\
Machine learning Nanodegree\\
Topics Covered - Supervised learning, Unsupervised Learning, Reinforcement Learning, Deep Learning\\
\\
{\bf Relevant MOOCs }\textit{ (uncertified)}\\
Stanford CS224D (NLP), Stanford CS231N (Computer Vision), Algorithms(MIT OCW)

\end{rSection}

\end{document}
